---
title: "Basic usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic usage}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
lightbox: true
---

```{r setup}
library(stashPlot)
library(ggplot2)
```

## Create some plots to save
```{r make_some_plots}
plot_stuff <-
    ggplot(mtcars, aes(x = mpg, y = wt)) +
    geom_point()

stash_plot(
    plot_stuff,
    plot_name = "mpg_wt"
)

plot_other_stuff <-
    ggplot(mtcars, aes(x = mpg, y = qsec)) +
    geom_point()

stash_plot(
    plot_other_stuff,
    plot_name = "mpg_qsec"
)

plot_more_stuff <-
    ggplot(mtcars, aes(x = mpg, y = disp)) +
    geom_point()

stash_plot(
    plot_more_stuff,
    plot_name = "mpg_disp"
)
```

## List off the plots we have saved
```{r list_plots}
list_plots()
```

## Display a plot by name
```{r display_plot}
get_plot("mpg_wt")
```

## Assemble plots into a figure
```{r assemble_plots}
gridExtra::grid.arrange(
    get_plot("mpg_wt", verbose = FALSE),
    get_plot("mpg_qsec", verbose = FALSE),
    get_plot("mpg_disp", verbose = FALSE),
    ncol = 2
)
```

## Modify a plot while assembling it
```{r modify_plot}
gridExtra::grid.arrange(
    get_plot("mpg_wt", verbose = FALSE) +
        labs(
            title = "Miles per gallon vs weight",
            x = "Amazing!",
            y = "Much Science!",
            caption = "meh"
            ) +
        theme_dark(),

    get_plot("mpg_qsec", verbose = FALSE) +
        theme(axis.text = element_text(size = 20)),

    get_plot("mpg_disp", verbose = FALSE) +
        theme_bw(),

    ncol = 2
)
```

## Import a plot that someone else made
```{r import_plot}
import_plot(
    qs_file = "mpg_wt_2024_09_18_11.52.53.qs",
    user = "Ryan"
)
```

## Import a bunch of plots from another folder

### lets make some plots in a different folder
```{r make_plots_in_other_folder}
stash_plot(
    ggplot(mtcars, aes(x = as.factor(cyl), y = wt)) + geom_point(),
    plot_name = "other_plot_1",
    figures_dir = "output/other_folder"
)

stash_plot(
    ggplot(mtcars, aes(x = as.factor(cyl), y = qsec)) + geom_point(),
    plot_name = "other_plot_2",
    figures_dir = "output/other_folder"
)
```

## Import all plots from another folder
This will not overwrite the files for any newer plots and those will be skipped
```{r import_all_plots}
import_all_qs_plots(
    from_figures_dir = "output/other_folder",
    user = "Ryan"
)

list_plots()
```

## Import all plots from another folder and overwrite newer
This will overwrite the files for any newer plots
```{r import_overwrite_plots}
import_all_qs_plots(
    from_figures_dir = "output/other_folder",
    user = "Ryan",
    overwrite_newer = TRUE
)
```

## Remove a plot
```{r remove_plot}
list_plots()

remove_plot("mpg_wt")

list_plots()
```